%Introduction

\section{Abstractions}

The architecture of the \textsc{Test Stand} consist in at leas three stand alone modules, that establish a mono-directional communication flow. But what exactly is a module? Chapter \ref{chap:heaven} reports some requirements which directly affect the implementation experience of \namens : [R.10] i.e. the need of an \textit{Extendible Design} and [R.11], which states the necessity of an \textit{Event-base architecture} to properly face RSP Engines, which exploit this kind of communication pattern.

Developing an \textit{Extendible} \textsc{Test Stend} which can handle any RSP Engine requires to start from two abstractions:
\begin{itemize}
\item \textit{Event Processor}
\item \textit{Event}
\end{itemize} 

The \textit{Event Processor} guarantees the system to be modular, because it simplify the behaviour of each component of the \textsc{Test Stand} structure, stereotyping the way of interaction. The \textit{Event} abstraction is required to define the head of the communication. \textsc{Test Stand} handle many communication flows, practically one for each module. Next section about data clarify how the communication is structured and we detail consequently how the components communicates.

Thus, to answer the question above, a module is an \textit{Event Processor} which can be positioned everywhere in the pipeline which represent the \textsc{Test Stand} architecture. 
As a matter of facts, specific implementations of modules reduce the generality of this definition and also the flexibility of the modules themselves.	

\section{Data}\label{sec:data-impl}

The Experiment data properties
The output data implementation

\section{Test Stand}\label{sec:teststand}

Event processor interface
Event Interface

\subsection{Streamer}

The NT File format
NTStreamer
FlowStream

\subsection{Result Collector} 

\section{Baselines}\label{sec:baselines-impl}

the RSPEngine Interface
Jena Integration
Esper Integration

Event implementation Graph or Statement or Serialised

\section{Analyser}\label{sec:analyser-impl}

port processing package



